An improved metric for the analysis of swarms

### 2017-12-06 paper.tex
Terminology

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
An important criteria in the application of swarm coordination algorithms is the extent to which they cause unnecessary movement. i.e. movement which occurs as a side affect of the algorithm rather than the the intended function. This paper examines the widely used distance metric as a mechanism to measure the internal movement of agents and introduces a new \emph{magnitude based metric}.

@@

\section{Repulsion/Cohesion based metric\label{section:MagnitudeDynamics}}
An agent's resultant magnitude is identified by Gazi and Passino~\cite{GP:11} and Barnes et al~\cite{BFV:07} as a `resultant characteristic' of a swarm. The cohesion and repulsion between an agent $b$ and its neighbour $b'$ produce a resultant vector. The vector is calculated by adding the cohesion effect and the repulsion effect.

The repulsion/cohesion based internal movement (\emph{Repulsion/Cohesion metric}) is measured by identifying the balance between the repulsion and cohesion vectors between agents as shown in Equation~\ref{eq:CohesionRepulsion}. This is derived from the \emph{inter-agent magnitude} as shown in Equation~\ref{eq:BotStabilityT}. `Jitter' in the case of the agent resultant \emph{Repulsion/Cohesion metric} is measured as the deviation created by the inter-agent relationships. The identification of this deviation produces the clarifying component of the agent \emph{Repulsion/Cohesion metric}.
%% The magnitude based metric identifies the resultant internal magnitude (vector magnitude) through the cohesive and repulsive magnitudes that exist between each agent pair in a swarm. 
An agent's resultant vector magnitiude is used as a scalar values to give an overall `size' to the agent relationship. The resultant scalar value is then modified based upon the `size' of the two relationship magnitudes.

@@

\section{Magnitude based internal movement model}\label{Section:StabilityModel}
Using the formulae for the calculation of cohesion~(Equation \ref{eq:FlyToCentre1}) and repulsion~(Equation \ref{eq:Repulsion1}) for every agent and its neighbours it is possible to calculate an \emph{agent resultant magnitude} value (sum of agent resultant magnitudes). This value represents the overall `potential' of an agent. This magnitude when normalised produces a component of the \emph{movement-destination vector} for a swarm. If the agent resultant magnitude is zero (null vector) then the agent will not move. $M(b)$ is the \emph{inter-agent resultant magnitude vector} for agent $b$ defined by:

\begin{equation}
\label{eq:BotStabilityT}
M(b) = k_cv_c(b) + k_rv_r(b)
\end{equation}

\begin{equation}
\label{eq:CohesionRepulsion}
P(b) = \left\{\begin{array}{lll}
               M(b)& if & k_cv_c(b) > k_r v_r(b)\\
              -M(b)& else
             \end{array}\right.
\end{equation}

>>>>

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEcompsoctitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
\IEEEcompsoctitleabstractindextext{%
\begin{abstract}
%\boldmath
An important criterion in the assessment of swarm coordination algorithms is the extent to which they cause unnecessary movement, i.e. movement which occurs as a side affect of the algorithm rather than the the intended function. This paper examines the widely used distance metric as a mechanism to measure the internal movement of agents and introduces a new \emph{cohesion/repulsion metric}.

@@

\section{Cohesion/repulsion metric\label{section:MagnitudeDynamics}}
An agent's \emph{resultant magnitude} is identified by Gazi and Passino~\cite{GP:11} and Barnes et al~\cite{BFV:07} as a `resultant characteristic' of a swarm. The sum of the cohesion and repulsion vectors between an agent $b$ and a neighbour $b'$ produce a resultant vector.

The cohesion/repulsion internal movement (\emph{cohesion/repulsion metric}) is measured by identifying the balance between the cohesion and repulsion vectors between agents as shown in Equation~\ref{eq:CohesionRepulsion}. This is derived from the \emph{inter-agent cohesion/repulsion vector} as shown in Equation~\ref{eq:BotStabilityT}. `Jitter' in the case of the agent resultant \emph{cohesion/repulsion metric} is measured as the deviation created by the inter-agent relationships. The identification of this deviation produces the clarifying component of the agent \emph{cohesion/repulsion metric}.
%% The magnitude based metric identifies the resultant internal magnitude (vector magnitude) through the cohesive and repulsive magnitudes that exist between each agent pair in a swarm. 
An agent's resultant vector magnitiude is used as a scalar values to give an overall `size' to the agent relationship. The resultant scalar value is then modified based upon the `size' of the two relationship magnitudes.

@@

\section{Cohesion/repulsion internal movement model}\label{Section:StabilityModel}
Section~ref{Section:StabilityMagnitude}~discussed calculation of resultant cohesion~(Equation \ref{eq:FlyToCentre1}) and resultant repulsion~(Equation \ref{eq:Repulsion1}) vectors for each agent deriving a combined \emph{cohesion/repulsion vector} via equation~\ref{eq:InterAgentMovement2}.

%% This value represents the overall `potential' of an agent. This vector when normalised produces a component of the \emph{movement-destination vector} for a swarm. If the total cohesion/repulsion vector is zero (null vector) then the agent will not move. $M(b)$ is the total \emph{cohesion/repulsion vector} for agent $b$ defined by:
%% 
%% \begin{equation}
%% \label{eq:BotStabilityT}
%% M(b) = k_cv_c(b) + k_rv_r(b)
%% \end{equation}

Now, we define for each agent $b$ a scalar, $P(b)$, a measure of the extent to which the neighbours of $b$ are cohering inwards or repelling outwards this is Equation~\ref{eq:CohesionRepulsion}.

\begin{equation}
\label{eq:CohesionRepulsion}
P(b) = \left\{\begin{array}{lll}
               |M(b)|& if & |k_cv_c(b)| > |k_r v_r(b)|\\
              -|M(b)|& otherwise
              \end{array}\right.
\end{equation}
